\texttt{davos}: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2022-11-21 paper/main.tex
tiny syntax update to main.tex

Although \texttt{davos} is designed to \textit{appear} to add a new
keyword to Python's vocabulary, this illusion is actually created through
several ``hacks'' that make use of the notebook's IPython backend
for processing and executing users' code.  Specifically, when
\texttt{davos} is first imported, or when it is activated after having been
set to an inactive state, two actions are triggered:  First, the
\texttt{smuggle()} function is injected into the IPython user
namespace.  Second, the \texttt{davos} parser is registered as a
custom IPython input transformer.

@@

Next, we load in the reformatted dataset (line 33) and pre-trained
model (line 35) that we wish to use in our analysis.  In our
hypothetical example, we can suppose that the model was provided as a
\texttt{scikit-learn} \texttt{Pipeline} object that passes data
through two pretrained models in succession.  First, a trained \texttt{CountVectorizer}
instance converts text data to an array of word counts.  Second, the
word counts are passed to a topic model~\cite{BleiEtal03} using a
pretrained \texttt{LatentDirichletAllocation} instance.
\begin{center}
\includegraphics[width=0.9\textwidth]{figs/example7}
\end{center}
Let us suppose that the \texttt{Pipeline} object had been saved by its
original creator using the \texttt{joblib} package, as
\texttt{scikit-learn}'s documentation recommends.  Because
\texttt{joblib} uses the \texttt{pickle} protocol internally, the
ability to save and load pre-trained models is not guaranteed across
different \texttt{scikit-learn} versions.  For example, suppose that
the \texttt{Pipeline} object was created using \texttt{scikit-learn}
v0.21.3.  In that version of \texttt{scikit-learn}, the
\texttt{LatentDirichletAllocation} class was defined in
\texttt{sklearn.decomposition.online\_lda}.  However, in version
0.22.0, that module was renamed to \texttt{\_online\_lda}, and in
version 0.22.1, it was again renamed to \texttt{\_lda}.

>>>>

Although \texttt{davos} is designed to \textit{appear} to add a new
keyword to Python's vocabulary, this illusion is actually created through
several ``hacks'' that make use of the notebook's IPython backend
for processing and executing users' code.  Specifically, when
\texttt{davos} is first imported, or when it is activated after having been
set to an inactive state, two actions are triggered.  First, the
\texttt{smuggle()} function is injected into the IPython user
namespace.  Second, the \texttt{davos} parser is registered as a
custom IPython input transformer.

@@

Next, we load in the reformatted dataset (line 33) and pre-trained
model (line 35) that we wish to use in our analysis.  In our
hypothetical example, we can suppose that the model was provided as a
\texttt{scikit-learn} \texttt{Pipeline} object that passes data
through two pretrained models in succession.  First, a trained \texttt{CountVectorizer}
instance converts text data to an array of word counts.  Second, the
word counts are passed to a topic model~\citep{BleiEtal03} using a
pretrained \texttt{LatentDirichletAllocation} instance.
\begin{center}
\includegraphics[width=0.9\textwidth]{figs/example7}
\end{center}
Let us suppose that the \texttt{Pipeline} object had been saved by its
original creator using the \texttt{joblib} package, as
\texttt{scikit-learn}'s documentation recommends.  Because
\texttt{joblib} uses the \texttt{pickle} protocol internally, the
ability to save and load pre-trained models is not guaranteed across
different \texttt{scikit-learn} versions.  For example, suppose that
the \texttt{Pipeline} object was created using \texttt{scikit-learn}
v0.21.3.  In that version of \texttt{scikit-learn}, the
\texttt{LatentDirichletAllocation} class was defined in
\texttt{sklearn.decomposition.online\_lda}.  However, in version
0.22.0, that module was renamed to \texttt{\_online\_lda}, and in
version 0.22.1, it was again renamed to \texttt{\_lda}.
